How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-10 analysis/paper/paper.Rmd
output plots
update from google docs

---
title: "How to use replication assignments for teaching integrity in empirical archaeology"
author:
  - Ben Marwick, bmarwick@uw.edu
  - Liying Wang
  - Ryan Robinson
  - Hope Loiselle
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r setup2, eval = FALSE}
# devtools::install_github("ekothe/rmdrive")
library(rmdrive)

@@

Archaeologists are increasingly adopting these practices also. For example… However current norms in teaching archaeology are out of step with these practices. Given shifts in community values, it is important that we prepare our students with the skills necessary to fulfill these expectations of greater transparency and reproducibility in research. Here we propose a new type of assignment, the replication report, to better align the practice of teaching archaeology with the ideals of archaeological practise. The replication report assignment involves students analysing a published report to determine the main claims made by the authors of that report, students obtaining the data used by the authors, and analysing that data to determine if one or more of the authors’ claims are reliable.

In this paper we describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology. Our experience is based on an upper level archaeology class on stone artefact analysis taught at the University of Washington. The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities. The assignments include seminar notes, lecture quizzes, laboratory worksheets, and two longer empirical reports. For the term that we report here, the class had 16 students, a typical number for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington. Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills. We describe our assignment and discuss student feedback on the our implementation. Finally we offer recommendations for how to use replication reports to teach archaeology students.

@@

Definitions of ‘replication’ vary across difference research areas and sometimes confused with ‘reproducibility’. Some examples in different fields… Definitions of reproducibility vs replicability are contested, survey a few and then declare we will use the ones from here: http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm

What other fields already do this…
What journals require replication materials? And what exactly do they require?
What previous examples of replication assignments in other fields? What do they have in common? What are the typical and unusual elements?

LY- economics: Ball, R., & Medeiros, N. (2012). Teaching integrity in empirical research: A protocol for documenting data management and analysis. The Journal of Economic Education, 43(2), 182-189.   https://www.tandfonline.com/doi/abs/10.1080/00220485.2012.659647 https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf

HL- international studies: Janz, N. (2016). Bringing the gold standard into the classroom: replication in university teaching. International Studies Perspectives, 17(4), 392-407. https://doi.org/10.1111/insp.12104

RR - computer networking: Yan, L., & McKeown, N. (2017). Learning networking by reproducing research results. ACM SIGCOMM Computer Communication Review, 47(2), 19-26. https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf

LY - neuroscience: Millman, K. J., Brett, M., Barnowski, R., & Poline, J. B. (2018). Teaching computational reproducibility for neuroimaging. Frontiers in neuroscience, 12, 727. https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full

@@

Our replication report assignment consisted of three small, graded activities to scaffold the preparation of the final report. Each step was separated by one week to give students time to work. Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and during class meetings.

For the first step we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories. This list is updated regularly, but is not exhaustive and is currently online at https://github.com/benmarwick/ctv-archaeology Working in groups of 3-4 people, students selected a journal article from this list as their target article for this assignment. We encouraged them to choose a target article about a stone artefact analysis that looked interesting to them. We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article. We used Slack, a free cloud-based web application for team communication. The instructors were members of all the student group channels to give guidance and support good communication habits. Students were required to individually submit the full bibliographic reference for their target article to complete step one.

For step two of the assignment, students were required to discuss in their groups to identify 2-3 key claims made by the authors of their target article. They were told to study the data visualizations in the paper to identify which figures seem to give the best support to the authors' claims. Recreating these 1-2 key visualisations was a key task in the production of the final report. A second task for step two was for students to identify and obtain the raw data files of their target article. The list of articles that the students chose from only included articles for which data were openly available. This removed the need for students to contact authors to request data, which may have added the risk of a long wait, refusal to share, or no reply. To complete step two, each student was required to submit a short statement summarising the 2-3 key claims of their target paper, and the raw data file.

@@

In the time between students submitting their final report and the grades being released we administered an  survey to obtain feedback anonymously from the students. The purpose of the feedback survey was to collect information about how to improve the assignment for future classes, to understand the students’ experience of the assignment, and what value they perceive in replication skills for archaeology in general, and for them individually.

@@

The second step was mostly straightforward, with students engaging in discussion in class and on Slack to identify the 2-3 key claims of their target paper, and identify the data visualisation that provided the most relevant support to one or more of those claims. Identifying the data files was less straightforward, with about one third of students failing to correctly identify the data files accompanying their target article. We attribute this to the relatively low level of familiarity of the students in working with raw data, so they are not sure when they are looking at it, and the high degree of variability in how the target article authors make their data open. Some authors include their data as a file in the supplementary information attached to the article, while others deposit their files on an open data repository such as osf.io or figshare.com, and then cite the DOI to the files in their article. Where the data files were nested in several layers of folders, some students struggled to find them.

The ability to easily share screenshots on Slack was important to the success of the third step. Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualization using R would provide the foundation for succeeding in this step. However, we found that for some students this was not sufficient practice, and substantial instructor guidance was required to help them complete this step. At the completion of this step, the instructor met one on one with each group to check how successful they were producing a basic visualization using data from the target article, and to discuss the group's strategy to complete the report. This was the most time-consuming aspect of the assignment for the instructor, holding a one hour meeting with each of the five groups.

@@

Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices. We were also prepared for students to have no prior experience with replication report assignments. Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge. We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication reports used in teaching archaeology, and received no replies.

```{r}
library(tidyverse)
feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))

describe results of follow-up survey: https://canvas.uw.edu/courses/1272207/quizzes/1134059/statistics

Discussion and conclusion

Recommendations… future plans

@@

________________

Notes:

Target journal: Advances in Archaeological Practice - how to section 3500 words “clear, concise, step-by-step guidelines for successfully completing tasks that are or are becoming common practice”

Key papers to read and cite:

Ball, R., & Medeiros, N. (2012). Teaching integrity in empirical research: A protocol for documenting data management and analysis. The Journal of Economic Education, 43(2), 182-189. https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf

Toelch, U., & Ostwald, D. (2018). Digital open science—Teaching digital tools for reproducible and transparent research. PLoS biology, 16(7), e2006022. https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2006022

Medeiros, N., & Ball, R. J. (2017). Teaching Integrity in Empirical Economics: The Pedagogy of Reproducible Science in Undergraduate Education. https://scholarship.haverford.edu/cgi/viewcontent.cgi?article=1189&context=economics_facpubs

Hicks, S. C., & Irizarry, R. A. (2018). A guide to teaching data science. The American Statistician, 72(4), 382-391.

Janz, N. (2016). Bringing the gold standard into the classroom: replication in university teaching. International Studies Perspectives, 17(4), 392-407. https://doi.org/10.1111/insp.12104

Jern, A. (2018). A preliminary study of the educational benefits of conducting replications in the classroom. Scholarship of Teaching and Learning in Psychology, 4(1), 64.

Çetinkaya-Rundel, M., & Rundel, C. (2018). Infrastructure and tools for teaching computing throughout the statistical curriculum. The American Statistician, 72(1), 58-65.

Yan, L., & McKeown, N. (2017). Learning networking by reproducing research results. ACM SIGCOMM Computer Communication Review, 47(2), 19-26. https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf

Millman, K. J., Brett, M., Barnowski, R., & Poline, J. B. (2018). Teaching computational reproducibility for neuroimaging. Frontiers in neuroscience, 12, 727. https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full

Wessa, P. (2009). How Reproducible Research Leads to Non-Rote Learning within Socially Constructivist Statistics Education. Electronic Journal of e-Learning, 7(2), 173-182.

https://politicalsciencereplication.wordpress.com/2014/04/02/reproducibility-pioneers-political-scientists-assigning-replications-to-students/

https://www.washingtonpost.com/news/monkey-cage/wp/2014/02/12/replication-in-political-science-graduate-courses-an-untapped-resource/?noredirect=on&utm_term=.a557ce616b59

https://docs.google.com/forms/d/e/1FAIpQLSeRk7_4Rrzb3DafYGD4NYFjlNJ1rct50iPzzsEuxk6kiID-ag/viewform

Apply for Sloan foundation for a survey and study of data availability https://sloan.org/programs/digital-technology/scholarly-communication https://sloan.org/grants/apply#tab-letters-of-inquiry
________________

For each case study of a class that uses a replication assignment, we want to know

Variable
	Ball and Medeiros (2012)
	Ball (2018)
	Janz 2016
	Millman et al.(2018) 
	Yan & McKeown 2017
	etc
	How long (year/term/week)?
	A term

	8 weeks
	fall semester, 17 weeks 
	Three weeks

	How many students?
	NA

	~15

	200 students over 5 years

	Group or individual?
	individual

	individual
	group
	In pairs

	Main software tool (R/Python/??)?
	Stata

	R
	Python
	Amazon Web Services EC2

	Using Markdown/LaTeX/??
	NA
	R Markdown
	NA
	Markdown
	NA

	Using Git/GitHub or not?
	NA

	NA
	Git and GitHub
	NA

	Using CI (e.g. Travis) or not?
	NA

	NA
	Travis CI, Circle CI, and Appveyor
	No

	In class presentation or not?
	NA

	Yes
	Yes
	Yes

	Peer review by other students or not?
	NA

	Yes
	Yes
	Yes

	Students contact original study authors or not?
	NA

	Yes

	Yes

	Public posting of results by students (e.g. blog, osf.io, other repository) or not?
	Yes, Haverford College Library

	Yes

	Yes

________________

Notes on the background readings

Ball and Medeiros (2012)

To achieve the goal of fostering and teaching reproducible research, Ball and Medeiros (2012) developed a protocol for documenting statistical analyses for economics undergraduates to use for their empirical research projects. Instead of partial replication for final results, their 'soup to nut' approach suggests that the standards of replicability must contain four elements, including raw data files, associated metadata, all commands of data processing and analysis, and public availability. This approach establishes norms for complete documentation of empirical research to ensure researchers could successfully reproduce the results by reducing difficulties encountered during replication due to insufficient and partial sharing of data and analytical processes. Moreover, the transparency and reproducible of data bring important pedagogical benefits for students at all stages of completing their projects. Command files enable students to work with the data more efficient and have better data management by keeping track of each step they have done, and the most importantly, complete documentation of research helps students to take responsibility and accountability for their work.

Janz, Nicole. 2016. “Bringing the Gold Standard into the Classroom: Replication in University Teaching.” International Studies Perspectives 17: 392-407. 
·     Janz argues for bringing replication assignments into the graduate teaching program of political science
·     These assignments would do well in methods classes both to train in methods and to teach how to make work reproducible
·     In some courses for younger students, a duplication may be more beneficial, in upper level classes, a replication where original work is tested, plus new analyses or data can be added and potentially published
·     Replication studies allow a student to learn with original data, including bugs and flaws and to follow along the logic of the author
·     Teaches students how to make their own work reproducible in the future
·     Goes beyond literature review in helping students understand the field
·     This article addresses some criticisms as well: this does not promote error-hunting, and in fact, it was better for students when there were no errors, it does not hurt the reputation of other scientists, their work should be correct in the first place
·     Her class was interdisciplinary which she found very valuable for idea sharing, but difficult because people came in with different skill levels

Yan & McKeown (2017)
* The authors argue that replication assignments in graduate level courses provide more qualitative learning, inspire future research, and improve the networking community
* Networking graduate students at Stanford learn in a unique top-down manner that encourages them to learn the deeper mechanisms of the Internet
* Building from that approach, they were asked to create their own projects -- but these were lacking due to the time constraints of a term and overly ambitious projects
* Instead, students asked to replicate "classic" netowrking papers
* 200 students over 5 years (2012-2017), 40 unique papers reproduced & projects published on course blog
* Work emulated in Mininet or Mahimahi (or another emulator if the original authors did so)
* Students who fail to correctly replicate results are still considered successful if their results resemble the general shape of the original, or if they are able to reflect and identify their own mistakes
* The "large majority" finished their projects by correctly replicating the original results
* Peer review and peer replication: pairs will end the assignment by reproducing another pair's replication
* Primary reason for the project is unique educational and experiential value
* Recreating the experiment is time consuming but very fulfulling. Students learned the paper much better by immersing themselves in it
* Unexpectedly, this project contributes to networking community as students verify work or expose inconsistencies 
* Students acquire new professional skills that they otherwise would not have

>>>>

---
title: "How to use replication assignments for teaching integrity in empirical archaeology"
author:
  - Ben Marwick, bmarwick@uw.edu
  - Liying Wang
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r setup2, eval = FALSE}
gh repo: https://github.com/benmarwick/replicationteachingarchaeology
# devtools::install_github("ekothe/rmdrive")
library(rmdrive)

@@

Archaeologists are increasingly adopting these practices also. For example… However current norms in teaching archaeology are out of step with these practices. Given shifts in community values, it is important that we prepare our students with the skills necessary to fulfill these expectations of greater transparency and reproducibility in research. Here we propose a new type of assignment, the replication report, to better align the practice of teaching archaeology with the ideals of archaeological practise. The replication report assignment involves three key steps: 1) students analysing a published report to determine what are the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.

In this paper we describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology. Our experience is based on an upper level archaeology class on stone artefact analysis taught during the spring quarter of 2019 at the University of Washington. The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities. The assignments include seminar notes, lecture quizzes, laboratory worksheets, and two longer empirical reports. For the term that we report here, the class had 16 students, and one graduate student teaching assistant. THis is a typical size for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington. The background of our students are mostly in humanities with diverse level of statistical knowledge. Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills. We describe our assignment and discuss student feedback on our implementation. Finally we offer recommendations for how to use replication reports to teach archaeology students.

@@

What does Barba say about the Ddefinitions of ‘replication’ and ‘reproducibility’? https://arxiv.org/abs/1802.03311 ?

What are the definitions that we use? http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm

What other academic fields value replication? How? By their journals and their teaching methods

What journals require replication materials? Answers in https://politicalsciencereplication.wordpress.com/2018/07/14/replication-and-transparency-in-political-science-did-we-make-any-progress/  what materials exactly do they require? What do we know about how successful that is? Answers in https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/how-are-we-doing-data-access-and-replication-in-political-science/8EE49C7FE45B46F20A50D9271BB3AAC4 and https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/lessons-from-a-decade-of-replications-at-the-quarterly-journal-of-political-science/284B2830BFD99888B42D4CEABC28B9EE

What previous examples of replication assignments in other fields? ~3-6 sentences to summarise who/what/how/etc. of each one.

What are the typical and unusual elements for replication assignments in other fields?

Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge. We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication. However, we did receive some offers from researchers willing to share their data for future replication assignments. We replied that our assignment required students to find public open data linked to publications, and that privately circulated data would not satisfy our requirements.

@@

A brief discussion of our replication report assignment was announced at the beginning of the term to give students background about the purpose and concepts of replication and our expectations. Our replication report assignment consisted of three small, graded activities to scaffold the preparation of the final report. The first step started from week four and each step was separated by one week to give students time to work and submit their final reports due on week seven. Students were expected to work in groups of 3-4 people, but submit their assignments for each of the three steps and the final report individually. Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and collectively during class meetings. Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices. We were also prepared for students to have no prior experience with replication assignments.

For the first step we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories. This list is updated regularly, but is not exhaustive, and is currently online at https://github.com/benmarwick/ctv-archaeology. Working in groups of 3-4 people, students selected a journal article from this list as their target article for this assignment. We encouraged them to choose a target article about a stone artefact analysis that looked interesting to them. We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article. We used Slack, a free cloud-based web application for team communication, to help them collaborate with each other efficiently. The instructors were members of all the student group channels to supervise, give guidance and support good communication habits. Students were required to individually submit the full bibliographic reference for their target article to complete step one.

For step two of the assignment, students were required to discuss in their groups to identify 2-3 key claims made by the authors of their target article. They were told to study the data visualizations in the paper to identify which figures seem to give the best support to the authors' claims. Recreating these 1-2 visualisations was a key task for the students in the production of their final report. A second task for step two was for students to identify and obtain the raw data files of their target article. The list of articles that the students chose from only included articles for which data were openly available. This removed the need for students to contact authors to request data, which may have added the risk of a long wait for a favourable reply, refusal to share, or no reply. To complete step two, each student was required to submit a short statement summarising the 2-3 key claims of their target paper, and the raw data file.

@@

In the time between students submitting their final report and the grades being released we administered an online survey on Canvas to obtain feedback anonymously from the students. The purpose of the feedback survey was to collect information about how to improve the assignment for future classes, to understand the students’ experience of the assignment, and what value they perceive in replication skills for archaeology in general, and for them individually. They had one week to respond survey, which was not a requirement but we encouraged them to give their valuable feedback. The anonymous survey before releasing grade of replication assignment could reduce possible biases from subjective perception when knowing grade to ensure a more reliable feedback. After the online survey was finished, the instructor showed the results to students in a lecture and invited them to share their thoughts for some interesting observations.

@@

The second step was mostly straightforward, with students engaging in discussion in class and on Slack to identify the 2-3 key claims of their target paper, and identify the data visualisation that provided the most relevant support to one or more of those claims. Given that not all students have statistical background, the instructor covered some statistical methods they might encounter while reading during lecture, such as principal components analysis, to give them the mathematical concepts behind it. Identifying the data files was less straightforward, with about one third of students failing to correctly identify the data files accompanying their target article. We attribute this to the relatively low level of familiarity of the students in working with raw data, so they are not sure when they are looking at it, and the high degree of variability in how the target article authors make their data open. Some authors include their data as a file in the supplementary information attached to the article, while others deposit their files on an open data repository such as osf.io or figshare.com, and then cite the DOI to the files in their article. Where the data files were nested in several layers of folders, some students struggled to find them.

The ability to easily share screenshots on Slack was important to the success of the third step. Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualization using R would provide the foundation for succeeding in this step. We have expected that two accompanying lab reports that required to be written with R markdown would help them practice crucial code they might need later. For the lab reports, they used R markdown template we provided to complete tasks of reading data into R, basic data tidying, and data visualization by modifying sample code. However, we found that for some students this was not sufficient practice, and substantial instructor guidance was required to help them complete this step. At the completion of this step, the instructor met one on one with each group to check how successful they were producing a basic visualization using data from the target article, and to discuss the group's strategy to complete the report. This was the most time-consuming aspect of the assignment for the instructor, holding a one hour meeting with each of the five groups.

@@

Thirteen out of sixteen students completed an anonymous feedback survey that includes two single answer questions, five likert scale questions, and two open-ended questions. Single answer questions were designed to know students' prior experiences of replication assignment and using R language. Ratings for likert scale questions were on a 1 through 5 scale starting at "strongly agree" down to "strongly disagree" to understand students opinion and attitude toward replication assignment in archaeology. Two open-ended questions seek to know more about their thoughts for replication in the classroom in general.

Describe the two figures we have for this…

## Analysis of the students' grades for the replication assignment

We graded the students’ final submissions using a rubric with criteria that covered content, the introduction, methods, result, and conclusion sections, and style. In Figure \@ref(fig:rubric-scores) we show the distribution and means of student scores for each criterion. The two criteria showing the highest mean score are “Style: use commas and apostrophes correctly, and spell consistently”, and “Intro: has clear statement of the purpose of the report”. All students got a perfect score for these two criteria. High scores for the grammar criterion are expected because these reflect basic writing skills required for many undergraduate-level courses. Students are expected to have learned these in lower level classes before taking this class. The high scores relating to the introduction section may reflect the effectiveness of the scaffolding steps that focussed students on the specific purpose of the assignment . The lowest mean score is for “Content: minimum of 4 scholarly items in the reference list” that shows some people did not include four items. This might result from insufficient prior training in searching for scholarly publications, suggesting that although this is also a skill that should have been acquired before taking this class, many students remain weak at this task. A low mean is also evident for "Intro: has names, locations, and basic chronology of sites", because some students neglected to supply these archaeological details. Future use of this assignment will incorporate these low-scoring criteria into the scaffolding steps to emphasize their importance to students and give an opportunity for early feedback to students.

The criteria most relevant to the replication component of the assignment, in order from highest mean score to lowest, are "Content: submission includes Rmd file, Data file, and Word file",  "Conclusion: state whether the author’s claims appear to be robust, unreliable, etc","Results: includes 1-2 original plots & description of these", and "Methods: identify the specific results you will replicate". This suggests that we could help students to develop a better skills in narrating their process (writing about methods), and describing and interpreting their data visualizations. In future we may include more fundamental exercises focusing on these tasks in the scaffolding steps. Overall, we find that comparison of the scores for the replication criteria and other criteria shows there is no clear evidence that the replication component of this assignment lowers students’ grades. The two lowest scoring criteria are more generic research and writing skills rather than skills specific to the replication aspect of the assignment.

Caption: Here is the output from the Canvas grading rubric showing the scores for each student (one dot) and each criterion that we graded the assignment on. The red bar shows the mean score for each criterion.

## Discussion

What are the benefits of replication in the classroom?

What are the challenges of replication in the classroom?

What factors could influence the success of replication practice? Term, students’ background, familiarity with programming language, basic techniques and statistics teaching in classes, tutorials, choices of papers for replications

## Conclusion

What are our main findings?

What are the limitations of our study? Small sample size might affect statistical power, feedback survey as an assessment method might be subjective (comparison with grade ), control conditions: other factors that might have impact on the replication paper

What recommendations can we make to other archaeology instructors?
Learning motivation, understanding of statistics and principles behind graphs with some exercises

What will we do differently in the future?

## Acknowledgements

@@
